Numerical trajectory patterns of floating macroalgae

### 2021-01-25 thesis_chapter_3.Rmd
map problem sorted

---
title: 'Numerical trajectory patterns of floating macroalgae'
author:
- R Coppin^[University of the Western Cape]
- C Rautenbach^[South African Weather Service]
- AJ Smit^[University of the Western Cape]
output:
  word_document:
    reference_docx: markdown/frontiers_template.docx
  pdf_document:
    fig_caption: yes
  html_document:
bibliography: references.bib
csl: markdown/frontiers.csl.txt
---

@@

#library(computeMSD)
library(ggplot2)
library(rgdal)
library(tidyverse)
library(gridExtra)
library(ggpubr)
library(ggord)
library(vegan)
library(dplyr)
library(ggpubr)
library(maps)
library(flextable)
library(officer)
library(tidync)
library(tidyverse)
library(hexbin)
library(lubridate)

@@

```{r map, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Figure 1:Map of the study domain. This is a temporary map until issues with the map script are resolved."}
library(jpeg)
library(grid)
library(gridExtra)

map_chp3 <- rasterGrob(as.raster(readJPEG("map/tempmap_chapter3.jpg")))
ggarrange(map_chp3)
```

@@

```{r sim table, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Details for each simulation run for the study"}

@@

```{r morphology table, message=FALSE, warning=FALSE, include=TRUE, echo=FALSE, fig.cap="Table summarising the atrributes and estimates used to calculate the overall surface area of Kommetjie kelp individuals used in the various simulation."}
area_table <- read.csv("tables/chapter_3/area_table.csv", sep = ";")
area_table <- flextable(data = area_table)
area_table <- theme_zebra(area_table, odd_header = "transparent", even_header = "transparent")
area_table <- align(x= area_table, align = "center", part = "all")
area_table <- set_header_labels(area_table, Plant.characteristic = "Plant characteristic", Approximate.shape = "Approximate shape", Equation.used = "Equation Used", Plant.dimensions = "Plant dimensions")
area_table <- set_header_labels(area_table, Ac.Minimum = "Ac Minimum", Ac.Mean = "Ac Mean", Ac.Maximum = "Ac Maximum")
area_table <- set_table_properties(area_table, width = 1, layout = "autofit")
area_table <- set_caption(area_table, "Table 2:Summary of the atrributes and estimates used to calculate the overall surface area of Kommetjie kelp individuals used in the various simulation.")
area_table
```

@@

```{r, message=FALSE, warning = FALSE, include= TRUE, echo = FALSE, fig.height=8, fig.width=8}
library(jpeg)
library(grid)
library(gridExtra)

>>>>

---
title: 'Numerical trajectory patterns of floating macroalgae'
author:
- R Coppin^[University of the Western Cape]
- C Rautenbach^[South African Weather Service]
- AJ Smit^[University of the Western Cape]
output:
  html_document:
  word_document:
    reference_docx: markdown/frontiers_template.docx
  pdf_document:
    fig_caption: yes
    latex_engine: xelatex
bibliography: references.bib
csl: markdown/frontiers.csl.txt
---

@@

#library(computeMSD)
library(ggplot2)
library(rgdal)
library(tidyverse)
library(gridExtra)
library(ggpubr)
library(ggord)
library(mapproj)
library(vegan)
library(dplyr)
library(ggpubr)
library(maps)
library(flextable)
library(officer)
library(tidync)
library(tidyverse)
library(hexbin)
library(lubridate)

@@

```{r map, echo=FALSE, message=FALSE, warning=FALSE, strip.white=TRUE, fig.cap="Figure 1:Map of the study domain. This is a temporary map until issues with the map script are resolved."}
library(png)
library(grid)
library(gridExtra)

map_chp3A <- rasterGrob(as.raster(readPNG("map/chp3_mapA.png")))
map_chp3B <- rasterGrob(as.raster(readPNG("map/chp3_mapB.png")))

ggarrange(map_chp3A, map_chp3B, ncol = 1, nrow = 2, labels = "AUTO")
```

@@

```{r sim table, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Details for each simulation run for the study"}
set_flextable_defaults(fonts_ignore=TRUE)

@@

```{r morphology table, message=FALSE, warning=FALSE, include=TRUE, echo=FALSE, fig.cap="Table summarising the atrributes and estimates used to calculate the overall surface area of Kommetjie kelp individuals used in the various simulation."}

set_flextable_defaults(fonts_ignore=TRUE)

area_table <- read.csv("tables/chapter_3/area_table.csv", sep = ";")
area_table <- flextable(data = area_table)
area_table <- theme_zebra(area_table, odd_header = "transparent", even_header = "transparent")
area_table <- align(x= area_table, align = "center", part = "all")
area_table <- set_header_labels(area_table, Plant.characteristic = "Plant characteristic", Approximate.shape = "Approximate shape", Equation.used = "Equation Used", Plant.dimensions = "Plant dimensions")
area_table <- set_header_labels(area_table, Ac.Minimum = "Ac Minimum", Ac.Mean = "Ac Mean", Ac.Maximum = "Ac Maximum")
area_table <- set_table_properties(area_table, width = 1, layout = "autofit")
area_table <- set_caption(area_table, "Table 2:Summary of the atrributes and estimates used to calculate the overall surface area of Kommetjie kelp individuals used in the various simulation.")
area_table
```

@@

```{r, message=FALSE, warning = FALSE, include= TRUE, echo = FALSE, fig.height=8, fig.width=8}

library(jpeg)
library(grid)
library(gridExtra)
